\subsection{Theoretical comparison of general features} \label{section:featureanalysis}
The next step is to perform a theoretical comparison between the client-server model and the decentralized blockchain model. In this analysis the blockchain model is based on Ethereum, as it is used by another master thesis student, Axel Vallin, for implementation of another version of the system. This version is later compared to the centralized application, which was developed in this thesis work. The analysis considers both approaches from different perspectives and points of view in order to get better understanding about pros and cons, related to each approach, as well as the consequences with using them.

General trivia about Ethereum, which is quite important in order to grasp Ethereum and blockchain-related concepts, that are being touched upon in this analysis, is briefly described in the Appendix \ref{section:ether}. Readers, that are not familiar with Ethereum and blockchain networks in general, are strongly advised to read through the appendix before studying this analysis.

In order to get better picture from the economic perspective, Ether is typically converted to USD in the analysis. During the process of writing this thesis report, Ether price saw a couple of huge spikes and dips, which came at no surprise, knowing that Ether, along with other cryptocurrencies, is extremely volatile (as discussed in \ref{section:economics}). Therefore, for the purpose of consistency throughout the report, Ether price was assumed being equal to 700 USD. Usage of that rough approximation will be denoted with the star ($^\star$) notation in the report.

\input{theoretical_featureanalysis/thirdpartyinvolvement.tex}
\input{theoretical_featureanalysis/transparency.tex}
\input{theoretical_featureanalysis/encryption.tex}
\input{theoretical_featureanalysis/constraints.tex}
\input{theoretical_featureanalysis/reusability.tex}
\input{theoretical_featureanalysis/economicaspects.tex}
\input{theoretical_featureanalysis/enviromentalaspects.tex}



