\subsection{Blocket Secure Package} \label{section:securepackage}

In order to accomplish the goals, that were defined in Section \ref{section:purpose}, and demonstrate the outcomes of a theoretical analysis, two different implementations of the original \emph{\Gls{Blocket Secure Package}} \citep{securepackage} are compared to eachother in detail. Blocket Secure Package is a service (called Blocketpaketet in Swedish), provided by Blocket.se, which is a Swedish merchandise trading platform. It is widely used by both enterprises and regular people. Sometimes, the buyer and the seller are located in different regions of the country and the goods need to be sent by mail. This introduces a potential possibility for fraud, for example, if the buyer transfers the money, there is always a chance that the seller doesn't send the item to the buyer. Thus, the whole trading process is based on human trust, which should work in theory, but there are people out there, who, unfortunately, make a living out of scamming people. 

Blocket Secure Package addresses that problem. By using this service, seller and buyer agree on the terms for the transfer, the payment and the condition of the goods. Once the agreement is reached, the seller sends the parcel with the items via logistics company DBSchenker, which is responsible for the transfer of the parcel. Once the parcel arrives, the buyer pays for the item upon the receival at the service point. The funds are then transferred to Blocket, which holds the money until the buyer is satisfied with the condition of the item(s). Only then, the seller gets his money. If the buyer is not satisfied, or never receives his goods, the transaction is reversed and the buyer gets the money back from Blocket. In this case, Blocket acts as a the third party and governing body, that keeps the money until the transfer of goods is complete.

This service comes at a varied cost from around 12 USD and upwards, depending on the size and weight of the goods to be transferred. The costs for logistics and handling of payments are included in that price. From my personal experience, the service works great, but there are some potential issues that are associated with it, which are briefly discussed in Section \ref{section:theoanalysis}.




