\subsection{Guidelines for comparison} \label{section:guidelinesforcomparison}
In section ??, both Secure Package Systems are compared to eachother from different standpoints and quality attributes in a practical analysis. Usage of different technologies and methods imposes different constraints and consequences, which are going to be described in this analysis. The main guidelines for comparison and questions to be answered are:

\paragraph{Third party involvement, privacy and trust} 
What are the risks in handing data over to third party in the hybrid centralized version? How can personal data be misused (identity thefts, etc), when handed over to the third party? Can a decentralized network be trusted? Issues with transparency of a blockchain. Issues with anonymity of blockchain.

\paragraph{Encryption constraints and mechanism} 
Does the usage of blockchain limit the choice of encryption techniques? What encryption mechanism would be the most efficient for both systems?

\paragraph{Key storage and distribution} 
Discussion of the issues that are associated with storing keys on a database. Implementation of secure channels for key distribution in different approaches.

\paragraph{Attack exposure} 
Discussion of security concerns regarding possible hacker attack (from technical standpoint). Different types of attacks that the systems are exposed to.

\paragraph{System efficiency, data optimization and performance under increased traffic (scalability)} 
What is the maximum capacity of the systems? How well does the data need to be optimized before sending it for both approaches? Typical efficiency drawbacks, associated with each approach.

\paragraph{Implementation difficulties and approaches} 
What constraints are there, regarding the implementation of both systems? How the architecture needs to be build for both systems? How the nodes, transactions and mechanism of goods transfer is implemented in the systems?  How well do the sensor communication works?

\paragraph{Requirements and constraints} 
What hardware and software requirements are there for both versions? How do these requirements constrain the development.

\paragraph{Modifiability} 
How well can system be modified with additional features?

\paragraph{Maintenance}
How are the systems maintained? What are the issues?

\paragraph{Reusability} 
How can the systems be reused to build other similar applications?

\paragraph{Environmental issues} 
Issues, associated with mining of transactions for blockchain application. 

\paragraph{Economic perspective} 
What economic issues are associated with the systems, both from the third-party point of view and user's perspective. 

\paragraph{Usability} 
How does the service works from user perspective? User-friendliness of the systems in general.
